Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2019-11-01 paper/paper.tex
i moved out of order discussion to preeliminary section on problems

Generally speaking, a Jupyter notebook is a document mixing prose,
code, visualization, together with resources: source code, data,
media.  It consists of a collection of two types of cells, namely code
cells and text cells. The latter may contain text written in markdown,
possibly including formulas as well as figures. This structure
facilitates to guide students through a problem set. Usually, the code
in a notebook is intended to be executed in a linear fashion even
though this is not imposed by the notebook. In fact, the notebook
should invite students to experiment which implies the opening of new
cells and the execution of code written by the student. In this
process, out-of-order execution naturally occurs and can have side
effects which tend to confuse students. While the order of execution
of individual cells can be inferred by the sequence number attributed
to a cell once it has been executed, in particular beginners are not
aware of the problems that out-of-order execution can entail.

@@

>>>>

Generally speaking, a Jupyter notebook is a document mixing prose,
code, visualization, together with resources: source code, data,
media.  It consists of a collection of two types of cells, namely code
cells and text cells. The latter may contain text written in markdown,
possibly including formulas as well as figures. This structure
facilitates to guide students through a problem set.

@@

\section{Problems and pitfalls in using Jupyter notebook}
Usually, the code in a notebook is intended to be executed in a linear fashion even
though this is not imposed by the notebook. In fact, the notebook
should invite students to experiment which implies the opening of new
cells and the execution of code written by the student. In this
process, out-of-order execution naturally occurs and can have side
effects which tend to confuse students. While the order of execution
of individual cells can be inferred by the sequence number attributed
to a cell once it has been executed, in particular beginners are not
aware of the problems that out-of-order execution can entail.
